\subsection{Shape Regularity Measure}\mbox{}\\
    $\textit{Shape measure}$ offers an objective mathematical measure on the overall quality of an Finite Element mesh, and this is helpful to explore the simplex regularity and to improve the quality of shapes of the elements. Different definitions are used for shape measure to present the quality of simplex, and we simply introduce the $\textit{geometric shape measure} ~\mu({T})$ of simplex ${T}$,  the one we use in this paper.

    \paragraph{Simplex Diameter and Volume}\mbox{}\\
    Let ${T} \in\mathbb{R}^n$ be a k-simplex where $k \leqslant n$, with vertices ${x}_0, \cdots, {x}_k \in\mathbb{R}^n$. We let diam$({T})^k$ denote the diameter of ${T}$, and we define
    \begin{equation*}
    %\operator???
    \operatorname{diam}({T})^k = \max \| x_i - x_j \|, \qquad 0\leqslant i\leqslant j\leqslant k.
    \end{equation*}
    In other words, diam$({T})^k$ is the longest distance between two vertices of ${T}$, which is equivalent to the length of the longest edge of ${T}$. If ${T}$ is a single vertex, then diam$({T}) = 0$.\\

    \noindent
    Let vol$^k$(${T}$) denote k-dimensional volume of ${T}$. We have
    \begin{equation*}
    \operatorname{vol^k} ({T}) = \frac{1}{k!}\cdot|\det(x_1-x_0, x_2-x_0,\cdots, x_k-x_0)|
    \end{equation*}
    \noindent
    If k = 0, then ${T}$ is a 0-dimensional simplex, i.e., a vertex. Then clearly, diam(${T}$) = 0, and vol$^0 ({T})$ = 1, the vol$^0$ of a single vertex is one.

    
    \paragraph{Shape Measure}\mbox{}\\
    Simplex diameter and volume are important to introduce shape measures. Here we define the {geometric shape measure} $\mu({{T}})$ of a simplex ${T}$ by
    \begin{equation*}
    \mu({{T}}) = \frac{\operatorname{diam}({T})^k}{\operatorname{vol^k}({T})}, \quad\operatorname{vol^k(T) \neq 0}
    \end{equation*}
    If vol$^k(T)$ = 0, then we define $\mu({{T}}) = \infty$.\\
    
    To understand this definition, we can translate $\mu({{T}})$ as a measurement of how different the two variables, i.e. diam$({T})^k$ and vol$^k({T})$, are. For example, for a 3-dimensional simplex, i.e. a triangle, shape measure helps measure how narrow the triangle is. In other words, it measures how small the smallest angle of the triangle is. 

    \paragraph{Stability of a Simplex}\mbox{}\\
    The reason why we need shape measure is to help understanding whether a simplex $T$ is non-degenerate, and to quantify how degenerate or non-degenerate. Let $T$ be a k-dimensional simplex in $\mathbb{R}^n$. We say that a simplex $T$ is degenerate if and only if $\mu({T}) = \infty$, i.e. vol$_k(T) = 0$ approximating to 0.

    
    %???
    \begin{tikzpicture}
    \draw (0,0) -- (3,2) -- (5,0)-- (0,0);
    \draw (7,0) -- (10,1) -- (12,0)-- (7,0);
    %\path (1,1) coordinate (A) (2.5, 2.5) coordinate (B) (3, 1) coordinate (C)
    %\draw (A) -- (B) -- (C) -- cycle
    \end{tikzpicture}

    Observing two pictures above, we actually want the interior angles of the simple $T$, i.e. traingles in this example, to be uniformly bounded from zero. Thus vol$_2(T)$ will never go to 0.
    While cutting a simplex into smaller pieces, we want to keep those pieces uniformly bounded and avoid degenrate simplices. \\

    \begin{lemma*}
    If $T, T'$ are simplices that are congruent to each other, then $\mu(T) = \mu(T')$.
    \end{lemma*}
    \begin{proof}\mbox{}\\
    Since $T$ is congruent to $T'$, by definition, we have $T' = v + cQT$, where $c$ is scaling factor, $v$ is a translation vector and $Q$ is an orthogonal matrix. In fact, we will show that scaling, translation, roation or mirroring does not influence the shape measure of a simplex. 
    Suppose $diam(T)^k = ||x_i - x_j ||$, and $vol^k(T) = \frac{1}{k!}\cdot|\det(x_1-x_0, x_2-x_0,\cdots, x_k-x_0)|$.
    
    To be specific, when scaling a simplex $T$ by a non zero factor $c$ to obtain $T'$, we have 
    \begin{align*}
     vol^k(T') &= \frac{1}{k!}\cdot|\det(cx_1-cx_0, cx_2-cx_0,\cdots, cx_k-cx_0)| \\
               &= \frac{c^k}{k!}\cdot|\det(x_1-x_0, x_2-x_0,\cdots, x_k-x_0)| = c\cdot vol^k(T).
    \end{align*}
    Since it scales over all vertices, $diam(T')^k = c^k\cdot diam(T)^k$. Therefore, we see
    \begin{align*}
    \mu(T') = \frac{diam(T')^k}{vol^k(T')} = \frac{c^k\cdot diam(T)^k}{c^k\cdot vol^k(T)} = \frac{diam(T)^k}{vol^k(T)} = \mu(T)
    \end{align*}

    Moreover, translation over simplex $T$ by a nonsingular vector $v$ to obatin $T'$ will not influence the shape measure as well. In detail, we have
    \begin{align*}
    diam(T')^k &= ||(x_i + v) - (x_j + v)|| \\ 
               &= ||x_i - x_j|| = diam(T)^k \\
    vol^k(T') &= \frac{1}{k!}\cdot|\det((x_1+v) - (x_0+v), (x_2+v)-(x_0+v),\cdots,(x_k+v)-(x_0+v))|\\
              &= \frac{1}{k!}\cdot|\det(x_1-x_0, x_2-x_0,\cdots, x_k-x_0)| = vol^k(T)\\
    \mu(T') &= \frac{diam(T')^k}{vol^k(T')} = \frac{diam(T)^k}{vol^k(T)} = \mu(T)
    \end{align*}

    Consider rotating and mirroring $T$ by an orthogonal matrix $Q$ to obtain $T'$. Since $Q$ is an orthogonal matrix, $Q^T = Q^{-1}$. Therefore, we have
    \begin{align*}
    diam(T')^k &= ||Qx_i - Qx_j||\\
               &= ||x_i - x_j|| = diam(T)^k&&\\
    vol^k(T') = vol^k(Q\cdot T) &= \frac{1}{k!}\cdot |\det(Q(x_1-x_0), Q(x_2-x_0),\cdots, Q(x_k-x_0)|\\
                                &= \frac{1}{k!}\cdot|det(Q)|\cdot|\det(x_1-x_0, x_2-x_0, \cdots, x_k-x_0)|\\
                                &= \frac{1}{k!}\cdot|-1|\cdot|\det(x_1-x_0, x_2-x_0, \cdots, x_k-x_0)|\\
                                &= \frac{1}{k!}\cdot|\det(x_1-x_0, x_2-x_0, \cdots, x_k-x_0)| = vol^k(T)\\
    \text{Therefore, we have } \mu(T') &= \frac{diam(T')^k}{vol^k(T')}\\
    &= \frac{diam(T)^k}{vol^k(T)} = \mu(T)
    \end{align*}
    Now we see that the shape measure is independent of scaling, translation, rotation or mirroring. Thus a simplex $T'$ which is obtained by these motions shares a same shape measure with $T$.
    
    [ORIGINAL: ]
    First, we show that volumes of k-simplices $T$ and $T'$ are the same, i.e. vol$^k (T)$ = vol$^k (T')$. By definition of congruence, we can see one difference between equality and congruence of two simplices is that congruence is independent of vertex ordering. Recall the definition of simplex volume. \(vol^k(T) = \displaystyle \frac{1}{k!}\cdot|det(x_1-x_0, x_2-x_0,\cdots, x_k-x_0)|\). Clearly, permutation of vertex $x_i$, where $0 \leq i \leq k$, will not influence the absolute value of the determinant. Both dividing by k!, we have vol$^k (T)$ = vol$^k (T')$.\\
    Moreover, by definition of congruence above, we can obatin $T'$ by applying rotation, mirroring, scaling, and translation over $T$. Thus, diam$(T')^k$, the longest distance between two vertices of $T'$, is equal to the longest distance between two vertices of $T$, diam$(T)^k$. Therefore, we have $\mu(T) = \frac{diam(T)^k}{vol^k(T)} = \frac{diam(T')^k}{vol^k(T')} = \mu(T')$.
    \end{proof}